Gut microbes and their genes are associated with cognition and neuroanatomy in children

### 2023-03-28 manuscript/main.tex
specify that the percentage is of the fitness-weighted importance

As with LMs, RF models for children under 6 months old
performed poorly (mean test-set correlation -0.12, mean RMSE 12.70),
but RFs were consistently able to learn the relationship between taxa
and cognitive function scores in children over 18 months of age (mean
test-set correlation 0.429, mean RMSE 17.29). For both age groups,
species that were important in RF overlapped with those that were
significant when testing the relationship with LMs (Figure
3A-B, Table S1A-B); except for \emph{Eubacterium ramulus}
all taxa that were significant using LMs belonged to a group
responsible for 80\% of the total relative importance in RF models
(Table 3, Figure 3A).
However, the rank-ordering of LM significance and RF importance
had substantive differences. For example, in children under 6 months,
only \emph{B. wexlerae} was significantly associated with cognitive function in LMs, but
was ranked 20th in importance for RF models.

>>>>

As with LMs, RF models for children under 6 months old
performed poorly (mean test-set correlation -0.12, mean RMSE 12.70),
but RFs were consistently able to learn the relationship between taxa
and cognitive function scores in children over 18 months of age (mean
test-set correlation 0.429, mean RMSE 17.29). For both age groups,
species that were important in RF overlapped with those that were
significant when testing the relationship with LMs (Figure
3A-B, Table S1A-B); except for \emph{Eubacterium ramulus}
all taxa that were significant using LMs belonged to a group
responsible for 80\% of the total fitness-weighted relative importance in RF models
(Table 3, Figure 3A).
However, the rank-ordering of LM significance and RF importance
had substantive differences. For example, in children under 6 months,
only \emph{B. wexlerae} was significantly associated with cognitive function in LMs, but
was ranked 20th in importance for RF models.
